Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
shorten Distance description

Besides a comparison between Rewinds and photos, our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media (Table \ref{table:betweensubjects}).
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters; and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

>>>>

Besides a comparison between Rewinds and photos, our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media (Table \ref{table:betweensubjects}).
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters so for analysis, these distances were logarithmically mapped to six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' The groups 0--6 were a distance of 0--10 meters, 10--100 meters, 100--1,000 meters, 1,000-10,000 meters, 10,000--100,000 meters, and over 100,000 meters from the user's home, respectively.
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}
